visualizemi: Visualization, Effect Size, and Replication of Measurement Invariance for Registered Reports

### 2024-10-19 appendix_1_fixrefs.Rmd
fixing supplement

---
appendix: "appendix_1.Rmd"
---

@@

@@

@@

>>>>

---
appendix: appendix_1.Rmd
bibliography: includes/references.bib
output: word_document
csl: "/Library/Frameworks/R.framework/Versions/4.4-arm64/Resources/library/papaja/rmd/apa7.csl"
---

@@

```{r echo = F, include = F}
library(dplyr)
library(lavaan)
library(visualizemi)
library(dmacs)
library(ggplot2)
library(papaja)
```

@@

```{r echo = F}
boot.partial.invariant <- readRDS("manu_data/boot.partial.invariant.RData")
```

@@

# References

<div id="refs"></div>

### 2024-10-19 appendix_2_fixrefs.Rmd
fixing supplement

---
appendix: "appendix_2.Rmd"
---

@@

>>>>

---
appendix: "appendix_2.Rmd"
bibliography: includes/references.bib
output: word_document
csl: "/Library/Frameworks/R.framework/Versions/4.4-arm64/Resources/library/papaja/rmd/apa7.csl"
---

@@

```{r}
library(dplyr)
library(lavaan)
library(visualizemi)
library(dmacs)
library(ggplot2)
library(papaja)
library(tidyr)
library(ggridges)
```

```{r setup, include=FALSE, echo = F}
knitr::opts_chunk$set(fig.path = as.character("figures/"))
knitr::knit('appendix_1_fixrefs.Rmd')
boot_rr_DF <- rio::import("manu_data/boot_rr_DF.csv")
boot.df.full <- rio::import("manu_data/boot_DF_full.csv")
boot.partial.summary.full <- rio::import("manu_data/boot_partial_summary_DF_full.csv")
boot.effects.summary.full <- rio::import("manu_data/boot_effects_summary_DF_full.csv")
```
